Dissecting Neural Style Transfer

### 2019-05-27 paper/paper.tex
1

To find more dislocators, let us consider \emph{how to describe a distribution} in general?
The obvious answer is then statistics, like mean, standard deviation,

>>>>

To find more dislocators, let us consider \emph{how to describe a distribution} in general?
The obvious answer is then sample statistics or estimators, like (sample) mean, (sample) standard deviation, 
(sample) skewness, (sample) kurtosis and any moments.
Unfortunately, we found that higher moments are too slow to compute for experiments,
so we ended up with the following (combinations) of sample statistics.
%\begin{enumerate}
%\end{enumerate}
